\texttt{dfoliatR}: An R package for detection and analysis of insect defoliation signals in tree rings

### 2020-09-14 dfoliatR_ms.tex
no real change

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"chguiterman/dfoliatR"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Load the package}
\KeywordTok{library}\NormalTok{(dfoliatR)}

\CommentTok{## Load data}
\KeywordTok{data}\NormalTok{(}\StringTok{"dmj_h"}\NormalTok{) }\CommentTok{# host tree series}
\KeywordTok{data}\NormalTok{(}\StringTok{"dmj_nh"}\NormalTok{) }\CommentTok{# non-host chronology}
\CommentTok{# View data structure for any data object via }
\CommentTok{# "View(dmj_h)" or "head(dmj_h)"}

\CommentTok{## Calculate indices, identify defoliation events}
\NormalTok{dmj_defol <-}\StringTok{ }\KeywordTok{defoliate_trees}\NormalTok{(}\DataTypeTok{host_tree =}\NormalTok{ dmj_h,}
                             \DataTypeTok{nonhost_chron =}\NormalTok{ dmj_nh,}
                             \DataTypeTok{duration_years =} \DecValTok{8}\NormalTok{,  }
                             \DataTypeTok{max_reduction =} \FloatTok{-1.28}\NormalTok{, }
                             \DataTypeTok{bridge_events =} \OtherTok{TRUE}\NormalTok{, }
                             \DataTypeTok{series_end_event =} \OtherTok{TRUE}\NormalTok{, }
                             \DataTypeTok{list_output =} \OtherTok{FALSE}\NormalTok{) }
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dmj_defol_stats <-}\StringTok{ }\KeywordTok{defol_stats}\NormalTok{(dmj_defol)}
\KeywordTok{View}\NormalTok{(dmj_defol_stats) }\CommentTok{# Table 1}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_defol}\NormalTok{(dmj_defol) }\CommentTok{# Fig. 1}
\CommentTok{## This creates a ggplot object. Additions can }
\CommentTok{## be made to adjust plotting themes and}
\CommentTok{## aesthetics, like color.   }
\CommentTok{## For more on the features of ggplot see}
\CommentTok{## https://ggplot2.tidyverse.org/}
\CommentTok{## Adding 'scale_color_manual()' will}
\CommentTok{## change the colors that denote }
\CommentTok{## the average NGSI value for each defoliation}
\CommentTok{## event.}
\KeywordTok{library}\NormalTok{(ggplot2)}
\KeywordTok{plot_defol}\NormalTok{(dmj_defol) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale_color_manual}\NormalTok{(}\DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\StringTok{"red"}\NormalTok{, }\StringTok{"orange"}\NormalTok{, }
                                \StringTok{"purple"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## Use the defol object "dmj_defol" created above}
\NormalTok{dmj_obr <-}\StringTok{ }\KeywordTok{outbreak}\NormalTok{(dmj_defol,}
                    \DataTypeTok{filter_min_series =} \DecValTok{3}\NormalTok{,}
                    \DataTypeTok{filter_min_defol =} \DecValTok{1}\NormalTok{,}
                    \DataTypeTok{filter_perc =} \DecValTok{25}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot_outbreak}\NormalTok{(dmj_obr, }\DataTypeTok{disp_index =} \StringTok{"GSI"}\NormalTok{) }\CommentTok{# Fig. 2}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dmj_obr_stats <-}\StringTok{ }\KeywordTok{outbreak_stats}\NormalTok{(dmj_obr)}
\KeywordTok{View}\NormalTok{(dmj_obr_stats) }\CommentTok{# Table 2}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{## calculate mean return interval for outbreak }
\CommentTok{## start years}
\NormalTok{intervals <-}\StringTok{ }\KeywordTok{diff}\NormalTok{(dmj_obr_stats}\OperatorTok{$}\NormalTok{start)}
\KeywordTok{mean}\NormalTok{(intervals) }\CommentTok{## 51.2 year mean return interval}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Alfaro1982}{}%
Alfaro, R., Sickle, G. van, Thomson, A., Wegwitz, E., 1982. Tree mortality and radial growth losses caused by the western spruce budworm in a Douglas-fir stand in British Columbia. Canadian Journal of Forest Research 12, 780--87.

@@

\leavevmode\hypertarget{ref-Zang2015}{}%
Zang, C., Biondi, F., 2015. \texttt{treeclim}: An R package for the numerical calibration of proxy-climate relationships. Ecography 38, 431--36, doi:\href{https://doi.org/10.1111/ecog.01335}{10.1111/ecog.01335}.

>>>>

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install\_github}\NormalTok{(}\StringTok{"chguiterman/dfoliatR"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#\# Load the package}
\KeywordTok{library}\NormalTok{(dfoliatR)}

\CommentTok{\#\# Load data}
\KeywordTok{data}\NormalTok{(}\StringTok{"dmj\_h"}\NormalTok{) }\CommentTok{\# host tree series}
\KeywordTok{data}\NormalTok{(}\StringTok{"dmj\_nh"}\NormalTok{) }\CommentTok{\# non{-}host chronology}
\CommentTok{\# View data structure for any data object via }
\CommentTok{\# "View(dmj\_h)" or "head(dmj\_h)"}

\CommentTok{\#\# Calculate indices, identify defoliation events}
\NormalTok{dmj\_defol \textless{}{-}}\StringTok{ }\KeywordTok{defoliate\_trees}\NormalTok{(}\DataTypeTok{host\_tree =}\NormalTok{ dmj\_h,}
                             \DataTypeTok{nonhost\_chron =}\NormalTok{ dmj\_nh,}
                             \DataTypeTok{duration\_years =} \DecValTok{8}\NormalTok{,  }
                             \DataTypeTok{max\_reduction =} \FloatTok{{-}1.28}\NormalTok{, }
                             \DataTypeTok{bridge\_events =} \OtherTok{TRUE}\NormalTok{, }
                             \DataTypeTok{series\_end\_event =} \OtherTok{TRUE}\NormalTok{, }
                             \DataTypeTok{list\_output =} \OtherTok{FALSE}\NormalTok{) }
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dmj\_defol\_stats \textless{}{-}}\StringTok{ }\KeywordTok{defol\_stats}\NormalTok{(dmj\_defol)}
\KeywordTok{View}\NormalTok{(dmj\_defol\_stats) }\CommentTok{\# Table 1}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot\_defol}\NormalTok{(dmj\_defol) }\CommentTok{\# Fig. 1}
\CommentTok{\#\# This creates a ggplot object. Additions can }
\CommentTok{\#\# be made to adjust plotting themes and}
\CommentTok{\#\# aesthetics, like color.   }
\CommentTok{\#\# For more on the features of ggplot see}
\CommentTok{\#\# https://ggplot2.tidyverse.org/}
\CommentTok{\#\# Adding \textquotesingle{}scale\_color\_manual()\textquotesingle{} will}
\CommentTok{\#\# change the colors that denote }
\CommentTok{\#\# the average NGSI value for each defoliation}
\CommentTok{\#\# event.}
\KeywordTok{library}\NormalTok{(ggplot2)}
\KeywordTok{plot\_defol}\NormalTok{(dmj\_defol) }\OperatorTok{+}
\StringTok{  }\KeywordTok{scale\_color\_manual}\NormalTok{(}\DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\StringTok{"red"}\NormalTok{, }\StringTok{"orange"}\NormalTok{, }
                                \StringTok{"purple"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#\# Use the defol object "dmj\_defol" created above}
\NormalTok{dmj\_obr \textless{}{-}}\StringTok{ }\KeywordTok{outbreak}\NormalTok{(dmj\_defol,}
                    \DataTypeTok{filter\_min\_series =} \DecValTok{3}\NormalTok{,}
                    \DataTypeTok{filter\_min\_defol =} \DecValTok{1}\NormalTok{,}
                    \DataTypeTok{filter\_perc =} \DecValTok{25}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{plot\_outbreak}\NormalTok{(dmj\_obr, }\DataTypeTok{disp\_index =} \StringTok{"GSI"}\NormalTok{) }\CommentTok{\# Fig. 2}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dmj\_obr\_stats \textless{}{-}}\StringTok{ }\KeywordTok{outbreak\_stats}\NormalTok{(dmj\_obr)}
\KeywordTok{View}\NormalTok{(dmj\_obr\_stats) }\CommentTok{\# Table 2}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#\# calculate mean return interval for outbreak }
\CommentTok{\#\# start years}
\NormalTok{intervals \textless{}{-}}\StringTok{ }\KeywordTok{diff}\NormalTok{(dmj\_obr\_stats}\OperatorTok{$}\NormalTok{start)}
\KeywordTok{mean}\NormalTok{(intervals) }\CommentTok{\#\# 51.2 year mean return interval}
\end{Highlighting}
\end{Shaded}

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-Alfaro1982}{}%
Alfaro, R., Sickle, G. van, Thomson, A., Wegwitz, E., 1982. Tree mortality and radial growth losses caused by the western spruce budworm in a Douglas-fir stand in British Columbia. Canadian Journal of Forest Research 12, 780--87.

@@

\leavevmode\hypertarget{ref-Zang2015}{}%
Zang, C., Biondi, F., 2015. \texttt{treeclim}: An R package for the numerical calibration of proxy-climate relationships. Ecography 38, 431--36, doi:\href{https://doi.org/10.1111/ecog.01335}{10.1111/ecog.01335}.
\end{cslreferences}
